\section{Background Estimations
\label{sec:background}}

Several SM processes can mimic the final-state signatures expected from leptoquark or top squark pair production and decay. In this dissertation, the backgrounds are divided into three groups, which are denoted as \ttbar irreducible, major reducible, and other. The \ttbar irreducible background comes from the pair production of top quarks when both the light lepton and \tauh are genuine, each produced from the decay of a \W boson. In this case, the light lepton can originate either directly from the \W boson decay or from a decay chain $\W \rightarrow \tau  \cPgn_{\tau} \rightarrow \ell\cPgn_{\ell} \cPgn_{\tau} \cPgn_{\tau}$. The major reducible background consists of events in which a quark or gluon jet is
misidentified as a \tauh. The processes contributing to the major reducible background are \W + jets, \Z + jets, and \ttbar. Additionally, a small contribution from the QCD multijet process is included, in which both the light lepton and the \tauh are misidentified jets. The contribution from QCD is only significant in the \etau channel of the leptoquark search. The third group, other backgrounds, consists of processes that make small contributions and may contain either genuine or misidentified tau leptons. The other backgrounds are estimated using the MC simulation, while the \ttbar irreducible and major reducible backgrounds are estimated using observed data. Both the major reducible and other backgrounds include events with both genuine and misidentified light leptons.

%This includes the diboson and single-top-quark processes, the \ttbar and \Z+jets processes when a light lepton is misidentified as a \tauh, and the \Z+jets process when the Z boson decays to a pair of tau leptons.

\input{ttbarbkg.tex}

\subsection{Major Reducible Background}

%\subsection{Reducible Background (QCD)}

\subsection{Other Backgrounds}

The \ttbar irreducible and major reducible backgrounds described above are the major backgrounds for the signal processes considered in this dissertation. Some background categories are not included in these data-driven estimations. These backgrounds contribute only a small number of events after the final selections. They are estimated from the simulation, normalized using the cross sections listed in Table \ref{tab:mcsamplesBG}. The contributions from the diboson and single-top-quark processes are entirely estimated using the simulation. Matching between the generator-level particles and the reconstructed tau object is used to identify the irreducible contribution from \Ztt + jets. The reducible contributions from \ttbar with two light leptons and \Zll + jets, when a light lepton is misidentified as a hadronic tau, are also estimated from the simulation.